Analysis of Crime Victims by Type and Gender from 2014 to 2023

### 2024-09-24 paper/paper.qmd
added reference to R for initial submission

In every society, keeping crime at a minimum has been a critical priority. Notably, certain demographic groups have been more affected by crime than others. For example, in the United States in 2008, there were a greater number of female nonfatal violent domestic violence victims than male ones (Catalano et al.). Similarly, Toronto is no exception to this phenomenon. The City of Toronto notes that certain groups of people are more susceptible to Gender-based violence than others.

@@

The remainder of the paper is structured as follows: Section 2 discusses the data; Section 3 presents the results; and Section 4 discusses our findings and highlights key weaknesses in the study.

@@

The variables of interest in the paper are CrimeType (named “CATEGORY” in the original dataset), which categories the type of crime into the four areas of Assault, Sexual Violation, Robberty and Other; AssaultType (named “ASSAULT_SUBTYPE” in the original dataset), which specifies assault on peace officers into the subtypes noted in the Introduction (INSERT LINK); Sex (named “SEX” in the original dataset), which is broken down into Male, Female and Unknown, where Unknown means the victim’s sex is not known by the Toronto Police Service; and Count, which notes the number of identified victims who share the same demographic characteristics reported in the dataset. Other characteristics such as age group, reported year and age cohort were not included as the variables were beyond the scope of the paper.

The paper uses the R programming language (insert citation) to analyze the dataset. The 'tidyverse' package was used to simulate the dataset and generate tests. The 'tidyverse' (Citation) and 'opendatatoronto' (citation) packages were used to download the Victims of Crime dataset. Then, the 'tidyverse' package (citation) was to clean and test the raw dataset. Finally, 'ggplot2' (citation), 'tidyverse' (citation), and 'scales' (citation) packages were used to create data visualization figures to highlight the results.

@@

After loading the dataset using the R programming language (citation), I used the 'tidyverse' (citation) package, and the 'ggplot2' (citation) package. The R code to do so was adapted from Alexander (insert citation).

@@

# Discussion

@@

## Data Attribution Statement {#sec-appendix-attributiojn}

@@

# References (To be added) {#sec-references}

>>>>

In every society, keeping crime at a minimum has been a critical priority. Notably, certain demographic groups have been more affected by crime than others. For example, in the United States in 2008, there were a greater number of female nonfatal violent domestic violence victims than male ones (Catalano et al. INSERT STATS). Similarly, Toronto is no exception to this phenomenon. The City of Toronto notes that certain groups of people are more susceptible to Gender-based violence than others.

@@

The remainder of the paper is structured as follows: @sec-data-overview discusses the data; @sec-data-results presents the results; and @sec-discussion discusses our findings and highlights key weaknesses in the study.

@@

The variables of interest in the paper are CrimeType (named “CATEGORY” in the original dataset), which categories the type of crime into the four areas of Assault, Sexual Violation, Robberty and Other; AssaultType (named “ASSAULT_SUBTYPE” in the original dataset), which specifies assault on peace officers into the subtypes noted in @sec-introduction; Sex (named “SEX” in the original dataset), which is broken down into Male, Female and Unknown, where Unknown means the victim’s sex is not known by the Toronto Police Service; and Count, which notes the number of identified victims who share the same demographic characteristics reported in the dataset. Other characteristics such as age group, reported year and age cohort were not included as the variables were beyond the scope of the paper.

The paper uses the R programming language [@citeR] to analyze the dataset. The 'tidyverse' package was used to simulate the dataset and generate tests. The 'tidyverse' (Citation) and 'opendatatoronto' [@opendatatoronto] packages were used to download the Victims of Crime dataset. Then, the 'tidyverse' package (citation) was to clean and test the raw dataset. Finally, 'ggplot2' (citation), 'tidyverse' (citation), and 'scales' (citation) packages were used to create data visualization figures to highlight the results.

@@

After loading the dataset using the R programming language [@citeR], I used the 'tidyverse' (citation) package, and the 'ggplot2' (citation) package. The R code to do so was adapted from Alexander (insert citation).

@@

# Discussion {#sec-discussion}

@@

## Data Attribution Statement {#sec-appendix-attribution}

@@

# References {#sec-references}
